Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution

### 2024-03-23 supp/supp.qmd
Some changes to supp for rendering

ggplot(countries) +
  geom_map(aes(map_id = country, fill = valid_percent*100), map = world_map) +
  geom_polygon(data = world_map, aes(x = long, y = lat, group = group), colour = 'black', fill = NA) +
  expand_limits(x = world_map$long, y = world_map$lat) +
  theme_void() + expand_limits(x = world_map$long, y = world_map$lat) +
  coord_fixed() + labs(fill="%") + theme_map(base_size = 22) + coord_map("moll")

@@

```{r, fig-gender}
#| label: fig-gender
#| fig-cap: Number of preprints published by male and female submitting authors.

@@

# Now we can use the first name and the country (that's important) to get an idea of the persons gender. 
  genders <- genderize(data2$submitting_author_firstname, country_id = data2$submitting_author_country_code, simplify = FALSE)
  write.csv(genders, here("data", "gender_dat.csv"))

@@

```{r, fig-citations}

@@

# Now we can plot the data
  cites <- ggplot(data_long_cites, aes(x = type, y = sqrt(citations))) +
  geom_violinhalf(aes(fill = type), flip = 1) + geom_jitter(shape=16, position=position_jitter(0.01), alpha = 0.2) + geom_line(aes(group = preprint_id), alpha = 0.2, colour = "black") +
  labs(x = "Paper Status", y = "Number of citations (sqrt transformed)") +
  theme_bw() + theme(legend.position = "none")
  cites

@@

  sum_cites2 <- data_long_cites  %>% tabyl(type, citations)

@@

Notably, published articles with zero citations dropped dramatically (`r sum_cites2[2,2]` papers; a `r 1 - (sum_cites2[2,2]/ sum_cites2[1,2])*100`% reduction) compared to preprints with zero citations, suggesting that once published, only `r sum_cites2[2,2]/ sum_cites2[1,2]*100`% had no citations.

Interestingly, highly a cited preprint did not necessarily become a highly cited published article over time, although some of this descrepency is related to whether and how preprints and articles are merged (Spearman Rank Correlation: `r spear$estimate`, S = `r spear$statistic`, *p* = `r spear$p.value`; @fig-citations).

```{r}

## References

>>>>

ggplot(countries) +
  geom_map(aes(map_id = country, fill = valid_percent*100), map = world_map) +
  geom_polygon(data = world_map, aes(x = long, y = lat, group = group), colour = 'black', fill = NA) +
  expand_limits(x = world_map$long, y = world_map$lat) +
  theme_void() + expand_limits(x = world_map$long, y = world_map$lat) +
  coord_fixed() + labs(fill="%") +  coord_map("moll")

@@

```{r, fig-gender}
#| label: fig-gender
#| fig-cap: Number of preprints published by male and female submitting authors. 
#| echo: false
#| include: false

@@

# Now we can use the first name and the country (that's important) to get an idea of the persons gender. 
  #genders <- genderize(data2$submitting_author_firstname, country_id = data2$submitting_author_country_code, simplify = FALSE)
 # write.csv(genders, here("data", "gender_dat.csv"))

@@

```{r, fig-citations} 
#| label: fig-citations
#| fig-cap: Number of citations to preprints and published articles that result from those preprints.

@@

# Now we can plot the data
  cites <- ggplot(data_long_cites, aes(x = type, y = sqrt(citations))) +
  geom_violinhalf(aes(fill = type), flip = 1) + geom_jitter(shape=16, position=position_jitter(0.01), alpha = 0.2) + geom_line(aes(group = preprint_id), alpha = 0.2, colour = "black") +
  labs(x = "Paper Status", y = "Number of citations (sqrt transformed)") +
  theme_bw() + theme(legend.position = "none")

@@

  sum_cites2 <- data_long_cites  %>% tabyl(type, citations)
```

@@

Notably, published articles with zero citations dropped dramatically (`r sum_cites2[2,2]` papers; a `r (1 - (sum_cites2[2,2]/ sum_cites2[1,2]))*100`% reduction) compared to preprints with zero citations, suggesting that once published, only `r sum_cites2[2,2]/ sum_cites2[1,2]*100`% had no citations.

Interestingly, a highly cited preprint did not necessarily become a highly cited published article over time, although some of this descrepency is related to whether and how preprints and articles are linked through crossref (Spearman Rank Correlation: `r spear$estimate`, S = `r spear$statistic`, *p* = `r spear$p.value`; @fig-citations).

# References
